Argennon: A Scalable Smart Contract Platform

### 2021-06-30 tex/sections/incentive.tex
Comment out a buggy part in the consensus
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Add incentives
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\note{TODO: update this section!}

\subsection{Transaction Fee}\label{subsec:transaction-fee}

>>>>

\subsection{Certificate Rewards}\label{subsec:rewards}

When the certificate of a committee of validators is included in a block, the signers of that certificate and the
delegates will be rewarded. Every validator will be rewarded equally. The delegates will be rewarded
proportional to the total stake of the signers of the certificate and their reward increases if the
certificate has more signers.

Rewards will not be distributed instantly, instead they will be distributed at the end of the staking period.
This will facilitate efficient implementations which avoid frequent updates in the AVM storage.
Rewards of every staking period depends on the amount of fees that are collected during that period.

\subsection{Stashing}\label{subsec:stashing}

If an account behaves maliciously, and that behaviour could not have happened due to a mistake, by providing a proof
in a block, the account will be disabled forever in the ARG smart contract. Disabling an account in the
ARG smart contract will prevent that account from signing any valid signature in the future.

Only behaviours will be stashed that can not happen due to a mistake or an attack. These behaviours include:
\begin{itemize}
    \item Signing a certificate for a block that is not conditionally valid.
    \item Signing a certificate for two different blocks at the same height if none of them
    is a fork block or a seal block.\footnote{signing
    a fork block and a normal block at the same height usually is a malicious behaviour. However, it will not be
    stashed because there are circumstances that a honest user could mistakenly do that.}
\end{itemize}

### 2021-06-30 tex/sections/persistence.tex
Add the reserve delegates concept
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Add the recovery protocol
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Add incentives
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

\subsection[Implementation]{Implementation Based on Vector Commitments}\label{subsec:impl-zk-edbs}

>>>>

\section{Storage Pages}\label{sec:storage-pages}

@@

\subsection{Vector Commitments}\label{subsec:impl-zk-edbs}

Informally, vector commitments allow committing to an ordered sequence of $q$ values
(i.e.\ a vector), rather than to single messages. This is done in a way such that it is later possible
to open the commitment with respect to specific positions (e.g., to prove that $m_i$ is the $i$-th committed
message). More precisely, vector commitments are required to satisfy what is called position binding.
Position binding states that an adversary should not be able to open a commitment to two different
values at the same position. While this property, by itself, would be trivial to realize using standard
commitment schemes, what makes vector commitments interesting is that they are concise, i.e.,
the size of the commitment string as well as the size of each opening \textbf{is independent of the
vector length}.
